---
title: "123Net FTTH Opportunity "
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bootswatch: minty
      primary: "#6CC3D4"
    orientation: rows
    vertical_layout: fill
runtime: shiny
resource_files:
  - MARKET_SIZING_SCRIPT_BLOCK_LEVEL_R2.csv
  - FULL_NETWORK_123NET_R2.kml
---

```{r, include=FALSE}
library(tidyverse)
library(flexdashboard)
library(crosstalk)
library(shiny)
library(shinythemes)
library(htmlwidgets)
library(sf)
library(leaflet)
library(leaflet.extras)
library(RColorBrewer)
library(tidycensus)
library(scales)
```


```{r, include=FALSE}

mi_fcc_stats <- read.csv('MARKET_SIZING_SCRIPT_BLOCK_LEVEL_R2.csv') %>% 
  mutate(GEOID = as.character(CENSUS_BLOCK),
         TOTAL_SERVED_LOCATIONS = TOTAL_RESIDENTIAL_LOCATION_IDS-UNSERVED_PLUS_UNDERSERVED,
         BEAD_PER_ROAD_MILE = ifelse(UNSERVED_PLUS_UNDERSERVED==0 | ROAD_MILES==0, 0, UNSERVED_PLUS_UNDERSERVED/ROAD_MILES),
         BEAD_ELIGIBLE = UNSERVED_PLUS_UNDERSERVED/TOT_HOUSING_UNITS_ACS_16_20) %>%
  mutate_if(is.numeric , replace_na, replace = 0) %>%
  filter(COUNTY_NAME %in% 
           c('ARENAC COUNTY',
             'BAY COUNTY',
             'CALHOUN COUNTY',
             'GENESEE COUNTY',
             'GRATIOT COUNTY',
             'INGHAM COUNTY',
             'ISABELLA COUNTY',
             'JACKSON COUNTY',
             'KALAMAZOO COUNTY',
             'KENT COUNTY',
             'LIVINGSTON COUNTY',
             'MACOMB COUNTY',
             'MASON COUNTY',
             'MIDLAND COUNTY',
             'MUSKEGON COUNTY',
             'OAKLAND COUNTY',
             'OTTAWA COUNTY',
             'SAGINAW COUNTY',
             'SHIAWASSEE COUNTY',
             'ST. CLAIR COUNTY',
             'WASHTENAW COUNTY',
             'WAYNE COUNTY',
             'ALLEGAN COUNTY',
             'BERRIEN COUNTY',
             'OCEANA COUNTY',
             'BARRY COUNTY',
             'BRANCH COUNTY',
             'CLINTON COUNTY',
             'EATON COUNTY',
             'IONIA COUNTY',
             'LAPEER COUNTY',
             'MONROE COUNTY',
             'VAN BUREN COUNTY'))

target_cnty_coverage <- mi_fcc_stats %>% summarise(TARGET_CNTY_LOCATIONS = sum(TARGET_LOCATION_IDS), .by = COUNTY_NAME)

mi_fcc_stats <- left_join(mi_fcc_stats, target_cnty_coverage, by = "COUNTY_NAME")

kml <- readr::read_file('FULL_NETWORK_123NET_R2.kml')
kml_file <- sf::read_sf('FULL_NETWORK_123NET_R2.kml')

options(tigris_use_cache = TRUE)
census_api_key('d2f0fe8f1e5a7984a67bbff53c703bc9c6ea9da9', install = TRUE, overwrite = TRUE)

# mi_county <- get_acs(geography = "block", 
#                      variables = "B23010_001",  #Households with children
#                      state = c("MI"),
#                      geometry = TRUE)

# vars <- load_variables(2020, "pl")
# View(vars)
# vars20 <- c("P005003", "P005004", "P005006", "P004003")
vars20 <- c("P1_001N")

mi_county <- get_decennial(geography = "block", 
                           variables = vars20, 
                           year = 2020,
                           summary_var = "P1_001N", 
                           state = "MI", 
                           geometry = TRUE) %>%
                    select(NAME,GEOID,geometry)
# P001001

# mi_county_df <- inner_join(mi_fcc_stats, mi_county, by = "GEOID") %>% distinct()
mi_county_df <- inner_join(mi_fcc_stats, mi_county, by = "GEOID") %>% distinct()

# %>% 
#   mutate(PCT_BEAD_ELIGIBLE = UNSERVED_WIRED_LOCATIONS/TOT_HOUSING_UNITS_ACS_16_20,
#          TARGET_ONNET = if_else(TARGET_ON_NET==1,"YES","NO"),
#          TARGET_EXPANSION_MARKETS = if_else(TARGET_EXPANSION_MARKETS==1,"YES","NO"),
#          ALL_TARGET_MARKETS = if_else(ALL_TARGET_MARKETS==1,"YES","NO"),
#          BEAD_PER_ROAD_MILE = sum(ifelse(UNSERVED_WIRED_LOCATIONS==0, 0, UNSERVED_WIRED_LOCATIONS))/sum(ROAD_MILES))

mi_county_sf <- sf::st_as_sf(mi_county_df)

# sd <- SharedData$new(fl_county_sf)

# kml_file <- '/cloud/project/summit.kml'
# kml_file <- sf::read_sf(kml_file)

st_crs(mi_county_sf) <- st_crs(kml_file)  # Set the CRS of stores_sf to match WGS 84 (EPSG: 4326)

# https://gis.stackexchange.com/questions/349955/getting-a-new-column-with-distance-to-the-nearest-feature-in-r
nearest <- st_nearest_feature(mi_county_sf,kml_file)
dist <- st_distance(mi_county_sf,kml_file[nearest,], by_element=TRUE)
pljoin <- cbind(mi_county_sf, st_drop_geometry(kml_file)[nearest,])
pljoin$dist <- dist/1609 # convert meters to milles
pljoin$dist <- gsub("\\[m\\]", "", pljoin$dist)
pljoin$dist <- as.numeric(pljoin$dist)
processed_df <- pljoin %>%
  mutate(dist_bin = ifelse(dist==0,"On-net",
                    ifelse(dist>0 & dist<=5,"Near-net (1 to 5 Miles)",
                    ifelse(dist>5 & dist<=10,"Off-net (6 to 10 Miles)",       
                            "Far Off-net (>10 Miles)"))),
         GEOID = as.factor(GEOID))

processed_df$dist_bin <- factor(processed_df$dist_bin)

# Define the desired order of levels
desired_order <- c("On-net", "Near-net (1 to 5 Miles)", "Off-net (6 to 10 Miles)")  # Modify this based on your actual bin labels
# Reorder the levels of the factor
processed_df$dist_bin <- factor(processed_df$dist_bin, levels = desired_order)


sd <- SharedData$new(processed_df)
```

BEAD Map {data-icon="fas fa-map-marked-alt"}
==================================================


Column {.sidebar data-width=450}
----------------------------------------------------


```{r}
# Create placeholder for the downloadButton
uiOutput("downloadUI")
```

```{r}
# Create the actual downloadButton
output$downloadUI <- renderUI( {
  # downloadButton("downBtn", "Download Data", style = "width:100%;")
  downloadButton("downBtn", "Download Data", style = "width:100%")
})

# Add download handling
output$downBtn <- downloadHandler(
  filename = function() {
    "mi_bead_analysis_data.csv"
  },
  content = function(file) {
    write.csv(mi_fcc_stats, file, row.names = FALSE)
  }
)
```

### <font size="5">**Filters**</font> 

```{r filter_1}

  filter_select(
  id = "county",
  label = "Select Counties:",
  sharedData = sd,
  group = ~COUNTY_NAME,
  allLevels = TRUE
  )
  
  filter_checkbox(
  id = "dist",
  label = "123Net Network Proximity(miles):",
  sharedData = sd,
  group = ~dist_bin,
  inline = FALSE,
  columns = 1
  )
  
  filter_slider("bead", "BEAD Locations Per Road Mile:", sd, "BEAD_PER_ROAD_MILE", round = TRUE)

```

<font size="3">**Data Sources and Definitions:**</font> 

- FCC's Broadband Data Collection (Jun. 2023, latest vintage).

- FCC's Unserved/Underserved Location Data (Oct. 2023).

- Road miles calculated using U.S. Census Bureau's Tiger/Line database for Rural/Urban functional system lane-length.

- BSL or Broadband Serviceable Location is defined as a residential address location that is served by 1 or more technologies as defined by the FCC.

- Total BEAD Eligible Locations include locations which are Unserved and Underserved and not "covered" by any other subsidy program.


Row
-----------------------------------------------------------------

### <font size="3">**Total Residential BSLs**</font>

```{r}
renderValueBox({
  
  vbox_1 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_1 <- round(sum(vbox_1$TOTAL_RESIDENTIAL_LOCATION_IDS),2)

valueBox(value = format(value_1, nsmall = 0, big.mark = ","), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

### <font size="3">**Total Served BSLs**</font>

```{r}
renderValueBox({
  
  vbox_2 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_2 <- round(sum(vbox_2$TOTAL_SERVED_LOCATIONS),2)

valueBox(value = format(value_2, nsmall = 0, big.mark = ","), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

### <font size="3">**Served BSLs %**</font>

```{r}
renderGauge({
  
  gauge_1 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
  
  value <- sum(ifelse(gauge_1$TOTAL_SERVED_LOCATIONS==0, 0, gauge_1$TOTAL_SERVED_LOCATIONS))/sum(gauge_1$TOTAL_RESIDENTIAL_LOCATION_IDS)
  
  if(!is.infinite(value) && !is.nan(value) && !is.na(value)) { 
  gauge(value*100, 
              min = 0, 
              max = 100, 
              symbol = '%',
              label = "Served BSLs %", 
              gaugeSectors(
                success = c(31, 100), 
                warning = c(26, 30), 
                danger = c(0, 25))
        )
  } else {
    gauge(value=0, 
              min = 0, 
              max = 100, 
              symbol = '%',
              label = "Served BSLs %", 
              gaugeSectors(
                success = c(31, 100), 
                warning = c(26, 30), 
                danger = c(0, 25))
        )
  }
        
})
```

### <font size="3">**BEAD Eligible Locations**</font>

```{r}
renderValueBox({
  
  vbox_3 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_3 <- round(sum(vbox_3$UNSERVED_PLUS_UNDERSERVED),2)

valueBox(value = format(value_3, nsmall = 0, big.mark = ","), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

### <font size="3">**BEAD Eligible Location %**</font>

```{r}
renderGauge({
  
  gauge_2 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
  
  value <- sum(ifelse(gauge_2$UNSERVED_PLUS_UNDERSERVED==0, 0, gauge_2$UNSERVED_PLUS_UNDERSERVED))/sum(gauge_2$TOTAL_RESIDENTIAL_LOCATION_IDS)
  
  if(!is.infinite(value) && !is.nan(value) && !is.na(value)) { 
  gauge(value*100, 
              min = 0, 
              max = 100, 
              symbol = '%',
              label = "BEAD Eligible %", 
              gaugeSectors(
                success = c(31, 100), 
                warning = c(26, 30), 
                danger = c(0, 25))
        )
  } else {
    gauge(value=0, 
              min = 0, 
              max = 100, 
              symbol = '%',
              label = "BEAD Eligible %", 
              gaugeSectors(
                success = c(31, 100), 
                warning = c(26, 30), 
                danger = c(0, 25))
        )
  }
        
})
```


### <font size="3">**BEAD Locations per Road Mile**</font>

```{r}
renderValueBox({
  
  vbox_5 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_5 <- round(sum(ifelse(vbox_5$UNSERVED_PLUS_UNDERSERVED==0 | vbox_5$ROAD_MILES==0, 0, vbox_5$UNSERVED_PLUS_UNDERSERVED))/sum(vbox_5$ROAD_MILES),1)

valueBox(value = format(value_5, nsmall = 0, big.mark = ","), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

Row
-----------------------------------------------------------------

### <font size="3">**Occupancy Rate**</font>

```{r}
renderValueBox({
  
  vbox_6 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_6 <- round(sum(ifelse(vbox_6$TOT_OCCP_UNITS_ACS_16_20==0, 0, vbox_6$TOT_OCCP_UNITS_ACS_16_20))/sum(vbox_6$TOT_HOUSING_UNITS_ACS_16_20),1)

valueBox(value = scales::percent(value_6, 0.1), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

### <font size="3">**Density (HUs per Road Mile)**</font>

```{r}
renderValueBox({
  
  vbox_7 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_7 <- round(sum(ifelse(vbox_7$TOT_HOUSING_UNITS_ACS_16_20==0, 0, vbox_7$TOT_HOUSING_UNITS_ACS_16_20))/sum(vbox_7$ROAD_MILES),1)

valueBox(value = format(value_7, nsmall = 0, big.mark = ","), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

### <font size="3">**Average Household Income**</font>

```{r}
renderValueBox({
  
  vbox_12 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_12 <- round(sum(ifelse(vbox_12$AGGREGATE_HH_INC_ACS_16_20==0, 0, vbox_12$AGGREGATE_HH_INC_ACS_16_20))/sum(vbox_12$TOT_HOUSING_UNITS_ACS_16_20),0)

valueBox(value = scales::dollar(value_12, big.mark = ","), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

### <font size="3">**Cable Competitors**</font>

```{r}
renderValueBox({
  
  vbox_8 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_8 <- round(mean(vbox_8$NUM_CABLE_COMPETITORS),1)

valueBox(value = format(value_8, nsmall = 0, big.mark = ","), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

### <font size="3">**FTTH Competitors**</font>

```{r}
renderValueBox({
  
  vbox_9 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_9 <- round(mean(vbox_9$NUM_FTTH_COMPETITORS),1)

valueBox(value = format(value_9, nsmall = 0, big.mark = ","), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

### <font size="3">**Copper Competitors**</font>

```{r}
renderValueBox({
  
  vbox_10 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_10 <- round(mean(vbox_10$NUM_COPPER_COMPETITORS),1)

valueBox(value = format(value_10, nsmall = 0, big.mark = ","), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

### <font size="3">**FWA Competitors**</font>

```{r}
renderValueBox({
  
  vbox_11 <- sd$data(withSelection = TRUE, withFilter = TRUE) 
    
  value_11 <- round(mean(vbox_11$NUM_FWA_COMPETITORS),1)

valueBox(value = format(value_11, nsmall = 0, big.mark = ","), icon = "fa-solid fa-house-chimney",  color = "primary")

})
```

Row
-----------------------------------------------------------------

### <font size="5">**BEAD Eligible Housing Units By Census Block & Network Proximity**</font>

```{r, include=TRUE}
renderLeaflet({
  
  map_df <- sd$data(withSelection = TRUE, withFilter = TRUE) 
  # %>% mutate(TOTAL_BEAD_LOCATIONS = ifelse(is.na(TOTAL_BEAD_LOCATIONS), 0, TOTAL_BEAD_LOCATIONS))
  
  minVal <- min(map_df$BEAD_PER_ROAD_MILE, na.rm = TRUE)
  maxVal <- max(map_df$BEAD_PER_ROAD_MILE, na.rm = TRUE)
  domain <- c(minVal,maxVal)

  # colorPal <- c(colorRampPalette(colors = c("#b2182b", "#b6f0b6"), space = "Lab")(abs(minVal)),
  #               colorRampPalette(colors = c("#b6f0b6", "#008000"), space = "Lab")(maxVal))
  
  colorPal <- c(colorRampPalette(colors = c("#b2182b", "#FFBB33"), space = "Lab")(abs(minVal)+1),
                colorRampPalette(colors = c("#FFBB33", "#008000"), space = "Lab")(maxVal))

   labels <- paste0(
    "<strong> County: </strong>",
    map_df$NAME, "<br/>",
    "<strong> Median Income: </strong>",
    scales::dollar(map_df$MED_HHD_INC_ACS_16_20, big.mark = ",", accuracy = 0.1), "<br/>",
    "<strong> HUs per Road Mile: </strong>",
    scales::comma(map_df$HHD_PER_ROAD_MILE, accuracy = 0.1), "<br/>",
    "<strong> BEAD Locations per Road Mile: </strong>",
    scales::comma(map_df$BEAD_PER_ROAD_MILE, accuracy = 0.1), "<br/>",
    "<strong> Cable Providers: </strong>",
    map_df$TOP_CABLE_PROVIDERS, "<br/>",
    "<strong> FTTH Providers: </strong>",
    map_df$TOP_FIBER_PROVIDERS, "<br/>",
    "<strong> Copper Providers: </strong>",
    map_df$TOP_COPPER_PROVIDERS, "<br/>",
    "<strong> FWA Providers: </strong>",
    map_df$TOP_FWA_PROVIDERS, "<br/>"
    ) %>%
    lapply(htmltools::HTML)
  
  
   leaflet() %>% 
    # setView(-77.0369, 38.9072, 12) %>%
    # addProviderTiles(providers$CartoDB.Positron) %>%
    addProviderTiles(provider = "OpenStreetMap", options = providerTileOptions(opacity = 1)) %>%
    addPolygons(
      data = map_df, 
      fillColor = ~ get('colorBin')(colorPal, domain)(BEAD_PER_ROAD_MILE), 
      weight = 1.5, 
      opacity = 1, 
      color = "white",
      fillOpacity = 0.5, 
      popup = labels
      ) %>%
    # addWebGLKMLHeatmap(kml, size = 20, units = "px") %>%
    addKML(
      kml,
      # markerType = "marker",
      stroke = TRUE, fillColor = "black", fillOpacity = 0, weight = 3,
      markerOptions = markerOptions(radius = 1)) %>%
    addLegend(
      position = "bottomright",
      pal = colorNumeric(colorPal, domain = domain),
      values = domain,
      bins = 10,
      title = "BEAD Locations per Road Mile",
      # labFormat = labelFormat(prefix = "$"),
      opacity = 1)
   
  })
```

Market Statistics {data-icon="fa-chart-bar"}
==================================================

```{r, include=FALSE}

pop20 <- get_decennial(
  state = "MI",
  geography = "county",
  variables = "P1_001N",
  year = 2020
)

pop10 <- get_decennial(
  state = "MI",
  geography = "county",
  variables = "P001001",
  year = 2010
)

pop10_clean <- pop10 %>%
  select(GEOID, value10 = value)

pop20 <- pop20 %>%
  select(GEOID, NAME, value20 = value)

county_joined <- pop20 %>%
  left_join(pop10_clean, by = "GEOID")

county_change <- county_joined %>%
  mutate(
    total_change = value20 - value10,
    percent_change = 100 * (total_change / value10)
  ) %>%
  filter(NAME %in% c(
            'Arenac County, Michigan',
             'Bay County, Michigan',
             'Calhoun County, Michigan',
             'Genesee County, Michigan',
             'Gratiot County, Michigan',
             'Ingham County, Michigan',
             'Isabella County, Michigan',
             'Jackson County, Michigan',
             'Kalamazoo County, Michigan',
             'Kent County, Michigan',
             'Livingston County, Michigan',
             'Macomb County, Michigan',
             'Mason County, Michigan',
             'Midland County, Michigan',
             'Muskegon County, Michigan',
             'Oakland County, Michigan',
             'Ottawa County, Michigan',
             'Saginaw County, Michigan',
             'Shiawassee County, Michigan',
             'St. Clair County, Michigan',
             'Washtenaw County, Michigan',
             'Wayne County, Michigan',
             'Allegan County, Michigan',
             'Berrien County, Michigan',
             'Oceana County, Michigan',
             'Barry County, Michigan',
             'Branch County, Michigan',
             'Clinton County, Michigan',
             'Eaton County, Michigan',
             'Ionia County, Michigan',
             'Lapeer County, Michigan',
             'Monroe County, Michigan',
             'Van Buren County, Michigan')
      )

pop20_state <- get_decennial(
  state = "MI",
  geography = "state",
  variables = "P1_001N",
  year = 2020
)

pop10_state <- get_decennial(
  state = "MI",
  geography = "state",
  variables = "P001001",
  year = 2010
)

pop10_state_clean <- pop10_state %>%
  select(GEOID, value10 = value)

pop20_state <- pop20_state %>%
  select(GEOID, NAME, value20 = value)

state_joined <- pop20_state %>%
  left_join(pop10_state_clean, by = "GEOID")

state_change <- state_joined %>%
  mutate(
    total_change = value20 - value10,
    percent_change = 100 * (total_change / value10)
    )

mi_vacancies <- get_decennial(
  geography = "county",
  variables = c(total_households = "H1_001N",
                vacant_households = "H1_003N"),
  state = "MI",
  year = 2020,
  output = "wide"
) %>%
  mutate(percent_vacant = 100 * (vacant_households / total_households))  %>%
  filter(NAME %in% c(
            'Arenac County, Michigan',
             'Bay County, Michigan',
             'Calhoun County, Michigan',
             'Genesee County, Michigan',
             'Gratiot County, Michigan',
             'Ingham County, Michigan',
             'Isabella County, Michigan',
             'Jackson County, Michigan',
             'Kalamazoo County, Michigan',
             'Kent County, Michigan',
             'Livingston County, Michigan',
             'Macomb County, Michigan',
             'Mason County, Michigan',
             'Midland County, Michigan',
             'Muskegon County, Michigan',
             'Oakland County, Michigan',
             'Ottawa County, Michigan',
             'Saginaw County, Michigan',
             'Shiawassee County, Michigan',
             'St. Clair County, Michigan',
             'Washtenaw County, Michigan',
             'Wayne County, Michigan',
             'Allegan County, Michigan',
             'Berrien County, Michigan',
             'Oceana County, Michigan',
             'Barry County, Michigan',
             'Branch County, Michigan',
             'Clinton County, Michigan',
             'Eaton County, Michigan',
             'Ionia County, Michigan',
             'Lapeer County, Michigan',
             'Monroe County, Michigan',
             'Van Buren County, Michigan')
         )

mi_state_vacancies <- get_decennial(
  geography = "state",
  variables = c(total_households = "H1_001N",
                vacant_households = "H1_003N"),
  state = "MI",
  year = 2020,
  output = "wide"
) %>%
  mutate(percent_vacant = 100 * (vacant_households / total_households)
         )
```

### <font size="3">**Population Change By County**</font>

```{r}
renderPlot({

  ggplot(county_change, aes(x = percent_change, y = reorder(NAME, percent_change))) +
  geom_col(fill = "navy", color = "navy", alpha = 0.5) +
  theme_minimal(base_family = "Verdana") +
  scale_x_continuous(labels = label_percent(scale = 1)) +
  labs(x = "Population Change Percent",
       y = "",
       title = "Population Change Percent In 123NET Target Expansion Counties",
       subtitle = "2020/2010 decennial US Census") +
  geom_vline(xintercept = 1.96) +
  annotate("text", x=1.6, y=10, label="+2% Michigan", angle=90, size = 5) +
  theme(text = element_text(size=18))
})
```

### <font size="3">**Household Vacancy Rate By County**</font>

```{r}
renderPlot({

  ggplot(mi_vacancies, aes(x = percent_vacant, y = reorder(NAME, percent_vacant))) +
  geom_col(fill = "navy", color = "navy", alpha = 0.5) +
  theme_minimal(base_family = "Verdana") +
  scale_x_continuous(labels = label_percent(scale = 1)) +
  labs(x = "Vacancy Rate Percent",
       y = "",
       title = "Vacancy Percent In 123NET Target Expansion Counties",
       subtitle = "2020 decennial US Census") +
  geom_vline(xintercept = 11.6) +
  annotate("text", x=11, y=10, label="11.6% Michigan", angle=90, size = 5) +
  theme(text = element_text(size=18))
})
```

